---
title: "BetterReg"
author: "Chris Aberson"
date: "2/20/2022"
output: md_document
---

title: 'BetterReg: An R package for Useful Regression Statistics'  
tags:  
  - R  
  - OLS Regression  
  - Logistic Regression  
authors:  
  - name: Christopher L. Aberson  
    orcid: 0000-0003-3481-7177  
    affiliation: 1  
affiliations:  
 - name: Cal Poly Humboldt  
   index: 1  
date: 20 February 2022  
bibliography: paper.bib  
---

# Summary

Statistics such as squared semi partial correlations, tolerance, and Mahalanobis Distances are useful for reporting the results of OLS Regression (e.g., @tabachnick_using_2019). Similarly values such as the Likelihood Ratio Chi-square (e.g., @cohen_applied_2015) and Likelihood R-square (@menard_logistic_2010). Such statistics are not part of base R (@r_core_team_r_2022) popular packages such *car* (@fox_r_2019). To fill these gaps, I developed BetterReg to provide these values. 

Squared semipartial correlations provide a measure of uniquely explained variances that is on the same scale as $R^2$ values. Tolerance values address multicollinearity by addressing variance unexplained in a predictor. Mahalanabis Distances are a popular measure of multivariate outliers that are presented on an $\chi^2$ scale. The Likelihood Ratio $\chi^2$ provides a significance test that is more stable than the commonly presented Wald Test for logistic regression. The Likelihood Ratio $\chi^2$ is the most widely recommended Pseudo $R^2$ statistic for logistic. 

# Useage

BetterReg functions require existing regression models (either OLS or Logistic for most statistics), dataset names (for some approaches), number of predictors (some functions), and desired amount of output (Mahal function). 

## *part* function for squared semipartial correlations 

The *part* function requires an existing LM model and indication of number of predictors. 
```{r}
library(BetterReg)
mymodel<-lm(y~x1+x2+x3+x4+x5, data=testreg)
parts(model=mymodel, pred=5)
```

## *tolerance* function for multicollinearity assumptions

The *tolerance* function requires only a model. 

```{r}
mymodel<-lm(y~x1+x2+x3+x4+x5, data=testreg)
tolerance(model=mymodel)
```

## *Mahal* function for detecting multivariate outliers

The *Mahal* function requires model, predictors, and desired number of values to output. 

```{r}
mymodel<-lm(y~x1+x2+x3+x4+x5, data=testreg)
Mahal(model=mymodel, pred=5, values=10)
```

## *LRchi* function for Logistic Regression Coefficients

The *LRchi* function takes input for the dependent variable name (y), up to 10 predictors (x1, x2, etc.), and the number of predictors. 

```{r}
LRchi(data=testlog, y="dv", x1="iv1", x2="iv2",numpred=2)
```

## *Pseudo* function for Logistic Regression Effect Size

The *Psuedo* function takes an existing model as input

```{r}
mymodel<-glm(dv~iv1+iv2+iv3+iv4, testlog,family = binomial())
pseudo(model=mymodel)
```

# References


